%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\projectTools}[1]{\textit{Tools: #1}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://deepank308.github.io/}{\Large Deepank Agrawal}} & GitHub profile: \href{https://github.com/Deepank308}{Deepank308}\\
  \href{mailto:deepank.361998@gmail.com}{deepank.361998@gmail.com} & {C/C++, Python, Javascript, Scala, Java, Bash}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{http://iitkgp.ac.in/}{Indian Institute of Technology Kharagpur}}{West Bengal, India}
      {B. Tech + M. Tech in Computer Science and Engineering;  GPA: 9.42/10.0}{July, 2017 -- May, 2022(expected)}
    \resumeSubheading
      {\href{http://tridentpublicschool.com/}{Trident Public School}}{Muzaffarpur, India}
      {Senior School Certificate Examination, CBSE; Percentage: 92\%}{June, 2015 -- March, 2017}
  \resumeSubHeadingListEnd

% %--------PROGRAMMING SKILLS------------
% \section{Programming Skills}
% {C/C++, Python, Javascript, Scala, SQL, Java, Bash}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://enthire.co/}{EntHire}}{San Francisco, CA}
      {Software Engineering Intern}{August, 2020 - September, 2020 \& December, 2020 - January, 2021}
      \resumeItemListStart
        \resumeItem{Chrome Extension}
          {\\
          Designed and developed a chrome extension to provide EntHire's smart hiring feature for LinkedIn hiring page. \\
          Executed with 100\% ownership and leaded the end-to-end API integration with the existing backend server. \\
          Played a vital role in expanding and strengthening the client base for EntHire platform. \\
          \projectTools{JS, Python, HTML5, CSS3, Node.js, jQuery, Webpack, Pyramid web framework}}
        \resumeItem{Backend deployment}
          {\\
          Deployed production server using AWS Elastic Beanstalk and built end-to-end data pipelines. \\
          Restructured database wrapper code by reasoning method utilities and shifting to latest API methods. \\
          \projectTools{Python, AWS, MongoDB, MySQL, Pyramid web framework}}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.ubc.ca/}{University of British Columbia}}{Vancouver, British Columbia}
      {Software Engineering Intern}{May, 2020 - July 2020}
      \resumeItemListStart
        \resumeItem{\href{https://www.pm.inf.ethz.ch/research/viper.html}{\textit{VIPER}} Program Verification}
          {\\
          Developed AST traversal logic for adding and modifying compile-time Scala generated VIPER elements. \\ 
          Reduces the time vested in Flows reasoning logic, from approx. 10 hours to an hour, for research experimentation. \\ \projectTools{Scala, Software Verification, Compiler Design, Object Oriented Programming, Graph Reasoning}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/Deepank308/Advance-OS-Assignments/tree/main/ass2}{Simple File System}}
      {Built a simple file system based on ext3 file system with an emulated in-memory disk in \textbf{C}.}
    \resumeSubItem{\href{https://github.com/Deepank308/Advance-OS-Assignments/tree/main/ass1-partb}{Loadable Kernel Module}}
      {Developed a simple interactive loadable kernel module that provides the functionality of a heap inside the kernel space. Handles concurrency, mutual exclusion, process \& memory management, and io-control.}
    \resumeSubItem{\href{https://github.com/Deepank308/Reliable-Communication-Protocol}{Reliable Communication Protocol}}
      {Developed a library for Transport Layer protocol to support loss-less communication, built on top of UDP layer using system-level UNIX signal handlers in \textbf{C}.}
    \resumeSubItem{\href{https://github.com/Deepank308/Operating-Systems}{UNIX Shell CLI}}
      {Implemented a UNIX shell that runs on top of the Linux kernel. Includes features like forking, I/O redirection and pipe-lining of processes in \textbf{C++}.}
    \resumeSubItem{\href{https://github.com/Deepank308/Operating-Systems}{CPU scheduler}}
      {Implemented a virtual round-robin CPU scheduler using POSIX threads and simulated a synthetic producer-consumer job mix on the scheduler in \textbf{C++}.}
    
  \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Awards \& Competition}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://www.facebook.com/codingcompetitions/hacker-cup/}{Facebook Hacker Cup 2020}}{Secured rank 592 in Round 1 and is among top 1742 candidates to qualify for Round 2}
    \resumeSubItem{\href{https://codingcompetitions.withgoogle.com/kickstart}{Google Kick Start 2020}}{Secured rank 165 and 95 in Round B and D respectively, among approx. 9000 candidates}
    \resumeSubItem{ACM ICPC 2019}{Ranked 50 at the Amritapuri Regionals. Ranked 51 among 4401 teams in the nation-wide prelims}
    \resumeSubItem{\href{http://www.igvc.org/}{IGVC 2019}}{Part of the team which was first to qualify and finished as runners-up in the Auto-Nav challenge}
    \resumeSubItem{JEE 2017}{AIR 15 among 1.4 million applicants in the JEE Mains. AIR 308 among 0.2 million applicants in the JEE Advanced examination}
    
  \resumeSubHeadingListEnd
  
 
%-----------EXTRA CURRICULAR ACTIVITIES-----------------
\section{Extra Curricular Activities}
  \resumeSubHeadingListStart
    \resumeSubItem{Sports Programming}{Solved over 600 programming problems and participated in over 100 online contests on various online judges like Codeforces, CodeChef, LeetCode. Codeforces handle: \href{http://codeforces.com/profile/bitfrost01}{bitfrost01}; CodeChef handle: \href{https://www.codechef.com/users/deepank15}{deepank15}}
    \resumeSubItem{IEEE Image Processing Winter Workshop}{Mentored a week-long workshop on image processing organized for 1st and 2nd year UG students with over 150 applicants. Taught basic image processing techniques using OpenCV and C++. Successfully guided 2 students through their final workshop project.}
    \resumeSubItem{\href{https://nss.gov.in/}{National Service Scheme}}{Worked as a volunteer helping local villagers in tree plantation, road construction. Participated in blood donation camp drives and also assisted in teaching local school children. Worked towards the betterment of nearby village - Gopali, coordinating with a team of 30 IIT Kharagpur students.}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
